--- 
title: "Desarrollo web en entorno servidor"
author: "Ricardo Pérez López"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
papersize: a4paper
lang: es-ES
subparagraph: true
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

For now, you have to install the development versions of **bookdown** from Github:

```{r eval=FALSE}
devtools::install_github("rstudio/bookdown")
```

```php
<?php

namespace app\models;

use yii\base\Model;
use yii\data\ActiveDataProvider;

/**
 * SocioSearch represents the model behind the search form about `app\models\Socio`.
 */
class SocioSearch extends Socio
{
    /**
     * {@inheritdoc}
     */
    public function rules()
    {
        return [
            [['id'], 'integer'],
            [['numero', 'telefono'], 'number'],
            [['nombre', 'direccion'], 'safe'],
            [['nombre', 'email'], 'safe'],
            [['borrado'], 'boolean'],
        ];
    }

    /**
     * {@inheritdoc}
     */
    public function scenarios()
    {
        // bypass scenarios() implementation in the parent class
        return Model::scenarios();
    }

    /**
     * Creates data provider instance with search query applied.
     *
     * @param array $params
     *
     * @return ActiveDataProvider
     */
    public function search($params)
    {
        $query = Socio::find();

        // add conditions that should always apply here

        $dataProvider = new ActiveDataProvider([
            'query' => $query,
        ]);

        $this->load($params);

        if (!$this->validate()) {
            // uncomment the following line if you do not want to return any records when validation fails
            // $query->where('0=1');
            return $dataProvider;
        }

        // grid filtering conditions
        $query->andFilterWhere([
            'id' => $this->id,
            'numero' => $this->numero,
            'telefono' => $this->telefono,
            'borrado' => $this->borrado,
        ]);

        $query->andFilterWhere(['like', 'nombre', $this->nombre])
            ->andFilterWhere(['like', 'direccion', $this->direccion])
            ->andFilterWhere(['like', 'email', $this->email]);

        return $dataProvider;
    }
}
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need to install XeLaTeX.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
